\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-12-05 paper/mswp2012-proposal.tex
Add reference to Nielsen

\begin{figure}[htb]
	\centering
		\includegraphics[width=0.6\textwidth]{images/method/prototyping}
	\caption{Horizontal and vertical prototyping \citep[Page 94]{DBLP:books/daglib/0076830}}
	\label{fig:prototyping}
\end{figure}

@@

Thinking Aloud is a method developed in the usability testing labs of IBM and is one of the most valuable usability engineering methods according to Nielsen. It involves participants thinking aloud as they perform certain tasks. The participants are asked to say whatever they are thinking about, looking at, doing or feeling while performing the tasks. Observers take notes of everything the participant says during the scenario without attempting to interpret their claims. The sessions are usually recorded to enable you to go back later and connect the claims with the tasks the participant was currently performing. The purpose of this method is to make assumptions explicit. By explicitely saying their thoughts, it gets easier to understand how the participants view the system and to identify their major misconceptions. It helps reveiling \emph{why} users do something. It is very important to integrate Thinking Aloud in a very early stage of the design and development process because early clues can help anticipating and tracing the source of problems.

@@

\begin{itemize}
\item Which techniques are already in use or have been introduced in the field of
\begin{itemize}
\item healthcare applications?
\item ubiquitous systems?
\item user centered design?
\item usability engineering?
\item ...
\end{itemize}
\item Which of the found techniques can be reused?
\item What can be improved?
\end{itemize}

>>>>

\begin{figure}[htb]
	\centering
		\includegraphics[width=0.6\textwidth]{images/method/prototyping}
	\caption{Horizontal and vertical prototyping \citep[Page 94]{nielsen1994}}
	\label{fig:prototyping}
\end{figure}

@@

Thinking Aloud is a method developed in the usability testing labs of IBM and is one of the most valuable usability engineering methods according to Jakob Nielsen \citep[Page 195ff]{nielsen1994}. It involves participants thinking aloud as they perform certain tasks. The participants are asked to say whatever they are thinking about, looking at, doing or feeling while performing the tasks. Observers take notes of everything the participant says during the scenario without attempting to interpret their claims. The sessions are usually recorded to enable you to go back later and connect the claims with the tasks the participant was currently performing. The purpose of this method is to make assumptions explicit. By explicitely saying their thoughts, it gets easier to understand how the participants view the system and to identify their major misconceptions. It helps reveiling \emph{why} users do something. It is very important to integrate Thinking Aloud in a very early stage of the design and development process because early clues can help anticipating and tracing the source of problems.

@@

\begin{itemize}
\item Which techniques are already in use or have been introduced in the field of
\begin{itemize}
\item healthcare applications?
\item ubiquitous systems?
\item user centered design?
\item usability engineering?
\end{itemize}
\item Which of the found techniques can be reused?
\item What can be improved?
\end{itemize}
